\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-24 tex/overview.tex
add equation reference
update transition

We use the fact that stability decomposes over the SCCs of a network to relate the robustness of a network to the robustness of its SCCs. To derive this relationship we substitute \ref{eq:singleresamplemutau} and \ref{eq:stabfactor} into \ref{eq:robustnessbygraph}, collect factors corresponding to components, decompose integrals into their respective products, collapse integrals over delta distributions, and cancel common factors between numerator and denominator.  Let $L$ denote the set of edges of $G$ that connect distinct SCCs.  Then, if $i \in C_\alpha$ for some SCC $C_\alpha$, we have
\begin{widetext}
\begin{equation}\label{eq:robustncessforsccs}
\begin{aligned}
\frac{\int d\mu(A) d\tau^{(1)}_i (A' \mid A) \mathcal{S}(A) \mathcal{S}(A')}
       {\int d\mu(A) \mathcal{S}(A)}
&= \frac{\begin{matrix}
  \int \prod\limits_{k \in C_\alpha} da_k\,d{a'}_k\, \rho(a_k)
    \rho_i({a'}_i) \prod\limits_{j \in C_\alpha \setminus i} \delta ({a'}_j - a_j)
    \mathcal{S}(\pi_{C_{\alpha}}(A)) \mathcal{S}(\pi_{C_{\alpha}}(A')) \times \\
 \prod\limits_{C_\beta \in \hier(G) \setminus C_\alpha} \int
   \prod\limits_{j \in C_\beta} da_k\,d{a'}_k\, \rho({a'}_j) \delta ({a'}_j - a_j)
      \mathcal{S}(\pi_{C_{\beta}}(A)) \mathcal{S}(\pi_{C_{\beta}}(A')) \times \\
 \prod\limits_{l \in L} \int da_l\,d{a'}_l\,\rho({a'}_l) \delta({a'}_l - a_l) \end{matrix}}
{\begin{matrix}\int \prod\limits_{k \in C_\alpha} da_k\,\rho(a_k) \mathcal{S}(\pi_{C_{\alpha}}(A)) \times \\
 \prod_{C_\beta \in \hier(G) \setminus C_\alpha}
   \int \prod\limits_{h \in C_\alpha} da_h,\rho(a_h) \mathcal{S}(\pi_{C_{\beta}}(A)) \times \\
 \prod\limits_{l \in L} \int da_l\,\rho(a_l) \end{matrix}} \\[1em]
&= \frac{\int \prod\limits_{k \in C_\alpha} da_k\,d{a'}_k\,\rho(a_k)
    \rho_i({a'}_i) \prod\limits_{j \in C_\alpha \setminus i} \delta ({a'}_j - a_j)
    \mathcal{S}(\pi_{C_{\alpha}}(A)) \mathcal{S}(\pi_{C_{\alpha}}(A'))}
{\int \prod\limits_{k \in C_\alpha} dk\, \rho(a_k) \mathcal{S}(\pi_{C_{\alpha}}(A))} \\
&= R(C_{\alpha}, S, \mu_\alpha, \tau^{(1)}_\alpha)
\end{aligned}
\end{equation}
\end{widetext}
where $\mu_\alpha$ and $\tau^{(1)}_\alpha$ refer to the analogues of \ref{eq:singleresamplemutau} for the subgraph $C_\alpha$ of $G$. \ref{eq:robustncessforsccs} shows that the terms in the sum over the elements of $A$, or equivalently the edges of $G$, that comprise a given SCC of $G$ reduce to the robustness of that SCC alone.  Likewise, when $i \in L$, we have
\begin{widetext}
\begin{equation}\label{eq:robustncessforsccconnect}
\begin{aligned}
\frac{\int d\mu(A) d\tau^{(1)}_i (A' \mid A) \mathcal{S}(A) \mathcal{S}(A')}
       {\int d\mu(A) \mathcal{S}(A)}
&= \frac{\begin{matrix}
  \prod\limits_{C_\alpha \in \hier(G)} \int
   \prod\limits_{j \in C_\beta} da_k\,d{a'}_k\, \rho({a'}_j) \delta ({a'}_j - a_j)
      \mathcal{S}(\pi_{C_\alpha}(A)) \mathcal{S}(\pi_{C_\alpha}(A')) \times \\
 \int da_i d{a'}_i \rho_i(a) \rho_a({a'}_i) \times
 \prod\limits_{l \in L\setminus i} \int da_l\,d{a'}_l\,\rho({a'}_l) \delta({a'}_l - a_l) \end{matrix}}
{\prod_{C_\alpha \in \hier(G)}
   \int \prod\limits_{h \in C_\alpha} da_h,\rho(a_h) \mathcal{S}(\pi_{C_\alpha}(A)) \times
 \int da_i \rho(a_i) \times
 \prod\limits_{l \in L \setminus i} \int da_l\,\rho(a_l)} \\
&= 1
\end{aligned}
\end{equation}
\end{widetext}
For each $C_{\alpha} \in \hier(G)$, there will be $d_\alpha$ values of $i$ such that $i \in C_{\alpha}$ requiring instances of \ref{eq:robustncessforsccs}; likewise, there will be $l$ values of $i$ such that $i \in L$ requiring instances of \ref{eq:robustncessforsccconnect}.  Hence, when we perform the summation over $i$ to compute the robustness of $\mathcal{F}/G$ for each $G$, we will obtain a weighted average:
\begin{equation}\label{eq:robschematic}
R = \frac{l+d_1 R_1 + d_2 R_2 + \cdots}{l+d_1 + d_2 + \cdots}.
\end{equation}
Here $R_\alpha$ is shorthand for $R(C_\alpha,S,\mu_\alpha,\tau^{(1)}_\alpha)$ and $R$ is shorthand for $R(G,S,\mu,\tau^{(1)})$.

@@

Since both numerator and denominator are linear in the variables $k_i$ over which we are optimizing, an elementary argument shows the quantity will assume its minimum value at one of the vertices of the simplex.
The value at the $i$-th vertex equals
\begin{equation}
 q_i =
 \frac{2 d_i (1 - R_i)}
      {(k_i - 1) v_i^2 + 2 d_i},
\end{equation}
hence the network which maximizes robustness will have as many SCCs as possible be of the type which have the smallest value of $q_i$.

>>>>

In this section we derive \ref{eq:robschematic}, which relates the dynamical robustness of a network to the dynamical robustness' of its SCCs and the number of links that connect distinct SCCs. We use the fact that stability decomposes over the SCCs of a network. More specifically, to derive this relationship we substitute \ref{eq:singleresamplemutau} and \ref{eq:stabfactor} into \ref{eq:robustnessbygraph}, collect factors corresponding to components, decompose integrals into their respective products, collapse integrals over delta distributions, and cancel common factors between numerator and denominator.  Let $L$ denote the set of edges of $G$ that connect distinct SCCs.  Then, if $i \in C_\alpha$ for some SCC $C_\alpha$, we have
\begin{widetext}
\begin{equation}\label{eq:robustncessforsccs}
\begin{aligned}
\frac{\int d\mu(A) d\tau^{(1)}_i (A' \mid A) \mathcal{S}(A) \mathcal{S}(A')}
       {\int d\mu(A) \mathcal{S}(A)}
&= \frac{\begin{matrix}
  \int \prod\limits_{k \in C_\alpha} da_k\,d{a'}_k\, \rho(a_k)
    \rho_i({a'}_i) \prod\limits_{j \in C_\alpha \setminus i} \delta ({a'}_j - a_j)
    \mathcal{S}(\pi_{C_{\alpha}}(A)) \mathcal{S}(\pi_{C_{\alpha}}(A')) \times \\
 \prod\limits_{C_\beta \in \hier(G) \setminus C_\alpha} \int
   \prod\limits_{j \in C_\beta} da_k\,d{a'}_k\, \rho({a'}_j) \delta ({a'}_j - a_j)
      \mathcal{S}(\pi_{C_{\beta}}(A)) \mathcal{S}(\pi_{C_{\beta}}(A')) \times \\
 \prod\limits_{l \in L} \int da_l\,d{a'}_l\,\rho({a'}_l) \delta({a'}_l - a_l) \end{matrix}}
{\begin{matrix}\int \prod\limits_{k \in C_\alpha} da_k\,\rho(a_k) \mathcal{S}(\pi_{C_{\alpha}}(A)) \times \\
 \prod_{C_\beta \in \hier(G) \setminus C_\alpha}
   \int \prod\limits_{h \in C_\alpha} da_h,\rho(a_h) \mathcal{S}(\pi_{C_{\beta}}(A)) \times \\
 \prod\limits_{l \in L} \int da_l\,\rho(a_l) \end{matrix}} \\[1em]
&= \frac{\int \prod\limits_{k \in C_\alpha} da_k\,d{a'}_k\,\rho(a_k)
    \rho_i({a'}_i) \prod\limits_{j \in C_\alpha \setminus i} \delta ({a'}_j - a_j)
    \mathcal{S}(\pi_{C_{\alpha}}(A)) \mathcal{S}(\pi_{C_{\alpha}}(A'))}
{\int \prod\limits_{k \in C_\alpha} dk\, \rho(a_k) \mathcal{S}(\pi_{C_{\alpha}}(A))} \\
&= R(C_{\alpha}, S, \mu_\alpha, \tau^{(1)}_\alpha)
\end{aligned}
\end{equation}
\end{widetext}
where $\mu_\alpha$ and $\tau^{(1)}_\alpha$ refer to the analogues of \ref{eq:singleresamplemutau} for the subgraph $C_\alpha$ of $G$. \ref{eq:robustncessforsccs} shows that the terms in the sum over the elements of $A$, or equivalently the edges of $G$, that comprise a given SCC of $G$ reduce to the robustness of that SCC alone.  Likewise, when $i \in L$, we have
\begin{widetext}
\begin{equation}\label{eq:robustncessforsccconnect}
\begin{aligned}
\frac{\int d\mu(A) d\tau^{(1)}_i (A' \mid A) \mathcal{S}(A) \mathcal{S}(A')}
       {\int d\mu(A) \mathcal{S}(A)}
&= \frac{\begin{matrix}
  \prod\limits_{C_\alpha \in \hier(G)} \int
   \prod\limits_{j \in C_\beta} da_k\,d{a'}_k\, \rho({a'}_j) \delta ({a'}_j - a_j)
      \mathcal{S}(\pi_{C_\alpha}(A)) \mathcal{S}(\pi_{C_\alpha}(A')) \times \\
 \int da_i d{a'}_i \rho_i(a) \rho_a({a'}_i) \times
 \prod\limits_{l \in L\setminus i} \int da_l\,d{a'}_l\,\rho({a'}_l) \delta({a'}_l - a_l) \end{matrix}}
{\prod_{C_\alpha \in \hier(G)}
   \int \prod\limits_{h \in C_\alpha} da_h,\rho(a_h) \mathcal{S}(\pi_{C_\alpha}(A)) \times
 \int da_i \rho(a_i) \times
 \prod\limits_{l \in L \setminus i} \int da_l\,\rho(a_l)} \\
&= 1
\end{aligned}
\end{equation}
\end{widetext}
For each $C_{\alpha} \in \hier(G)$, there will be $d_\alpha$ values of $i$ such that $i \in C_{\alpha}$ requiring instances of \ref{eq:robustncessforsccs}; likewise, there will be $l$ values of $i$ such that $i \in L$ requiring instances of \ref{eq:robustncessforsccconnect}.  Hence, when we perform the summation over $i$ to compute the robustness of $\mathcal{F}/G$ for each $G$, we will obtain a weighted average:
\begin{equation}\label{eq:robschematic}
R = \frac{l+d_1 R_1 + d_2 R_2 + \cdots}{l+d_1 + d_2 + \cdots}.
\end{equation}
Here $R_\alpha$ is shorthand for $R(C_\alpha,S,\mu_\alpha,\tau^{(1)}_\alpha)$ and $R$ is shorthand for $R(G,S,\mu,\tau^{(1)})$. \ref{eq:robschematic} demonstrates just as stability decomposes over the SCCs of a network architecture, which was shown in the previous section, so does dynamical robustness.

@@

Since both numerator and denominator are linear in the variables $k_i$ over which we are optimizing, an elementary argument shows the quantity will assume its minimum value at one of the vertices of the simplex.
The value at the $i$-th vertex equals
\begin{equation}\label{eq:robqual}
 q_i =
 \frac{2 d_i (1 - R_i)}
      {(k_i - 1) v_i^2 + 2 d_i},
\end{equation}
hence the network which maximizes robustness will have as many SCCs as possible be of the type which have the smallest value of $q_i$.
